Visualizing Example of Clustered Predicted TAD Boundary Regions

### 2019-08-17 Scripts/visualizing_example_predicted_tad_bounds.Rmd

ggplot(predprob_df_temp, aes(x=baseNum, y=PredProb)) +
     geom_line(size=.5)+
     #geom_smooth(method = "loess", size = 5, color="blue")
	   geom_vline(xintercept=predprob_df_temp$baseNum[which(predprob_df_temp$PredProb==1)], 
	              color="red", 
	              #linetype="dashed", 
	              size=.5)+
     geom_vline(xintercept=predprob_df_temp$baseNum[which(predprob_df_temp$predBound=="Yes")], 
	              color="blue", 
	              #linetype="dashed", 
	              size=.5)+
     xlab("Base Pair") +
     ylab("Predicted Probability") +
     theme_minimal() +
     theme_bw() +
     theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        #strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "bottom")

@@

xlabels <- c("1", "2", "3", "9", "10", "4", "5", "8", "6", "7")
fviz_dist(x, gradient = list(low = "white", mid = "pink", high = muted("red")))+
  xlab("")+
  ylab("")+
  #scale_fill_continuous("Distance")+
  scale_fill_gradient2("Distance",
                       low = "white", 
                       mid = "pink",
                       midpoint = 450000,
                       high = muted("red"))+
  scale_x_discrete(labels=xlabels)+
  scale_y_discrete(labels=xlabels)+
  theme_minimal()+
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        #panel.grid.major = element_blank(),
        #panel.grid.minor = element_blank(),
        #strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20))

hc1 <- hclust(x, method = "complete")
plot(hc1)

@@

k = which.max(z)+1
p <- pam(x, diss=TRUE, k=k, cluster.only=TRUE, trace.lev = 0)
clustdf <- data.frame(mid=predprob_df_temp$baseNum[which(predprob_df_temp$predBound=="Yes")], clust=cutree(hc1, k=k))

plot(hc1, hang = -1)
rect.hclust(hc1, k = k)

prob1intervals <- unique(clustdf$clust)
  mid2 <- numeric()
  for(i in prob1intervals){
    dat <- clustdf[which(clustdf$clust==prob1intervals[i]),]
    n=dim(dat)[1]
    mid2[i] <- ceiling((dat$mid[1]+dat$mid[n])/2)
  }

  predprob_df_temp$predBound2 <- ifelse(predprob_df_temp$baseNum %in% mid2, "Yes", "No")

ggplot(predprob_df_temp, aes(x=baseNum, y=PredProb)) +
     geom_line(size=.5)+
     #geom_smooth(method = "loess", size = 5, color="blue")
	   geom_vline(xintercept=predprob_df_temp$baseNum[which(predprob_df_temp$PredProb==1)], 
	              color="red", 
	              #linetype="dashed", 
	              size=.5)+
     geom_vline(xintercept=predprob_df_temp$baseNum[which(predprob_df_temp$predBound2=="Yes")], 
	              color="blue", 
	              #linetype="dashed", 
	              size=1)+
     xlab("Base Pair") +
     ylab("Predicted Probability") +
     theme_minimal() +
     theme_bw() +
     theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        #strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "bottom")

>>>>

dat1 <- predprob_df_temp[which(predprob_df_temp$PredProb==1),]

ggplot() + 
  geom_line(data=predprob_df_temp, aes(x=baseNum, y=PredProb), 
              color='black',
              size=.5)+
  geom_vline(data=dat1, aes(xintercept=baseNum, 
             color=as.factor(PredProb)),
             size=.75,
             show.legend = TRUE)+
  xlab("Base Pair") +
  ylab("Predicted Probability") +
  scale_color_manual(name = '', 
         values =c("red"),
         labels = c('Predicted Region'))+
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        #strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "bottom")

@@

xlabels <- c("1", "2", "3", "9", "10", "4", "5", "8", "6", "7")
fviz_dist(x, gradient = list(low = "white", mid = "pink", high = muted("red")))+
  xlab("Predicted Boundary Regions")+
  ylab("Predicted Boundary Regions")+
  #scale_fill_continuous("Distance")+
  scale_fill_gradient2("Distance\nBetween\nMidpoints",
                       low = "white", 
                       mid = "pink",
                       midpoint = 450000,
                       high = muted("red"))+
  scale_x_discrete(labels=xlabels)+
  scale_y_discrete(labels=xlabels)+
  theme_minimal()+
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        #panel.grid.major = element_blank(),
        #panel.grid.minor = element_blank(),
        #strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20))

hc1 <- hclust(x, method = "complete", size=2)
plot(hc1)

@@

k = which.max(z)+1
c <- clara(predprob_df_temp$baseNum[which(predprob_df_temp$predBound=="Yes")], k=k, metric = "euclidean",
           stand = FALSE, 
           trace = 2, medoids.x = TRUE)
clustdf <- data.frame(mid=predprob_df_temp$baseNum[which(predprob_df_temp$predBound=="Yes")], clust=c$clustering, medoid=ifelse(predprob_df_temp$baseNum[which(predprob_df_temp$predBound=="Yes")] %in% c$medoids, "Yes", "No"))

dend <- as.dendrogram(hc1)
dend %>% set("labels_col", c("red","green","red","red","green","red","green","red","red","green")) %>% set("labels_cex", 2) %>% plot(main = "Clustered Distances")
rect.hclust(hc1, k = k)

#prob1intervals <- unique(clustdf$clust)
#  mid2 <- numeric()
#  for(i in prob1intervals){
#    dat <- clustdf[which(clustdf$clust==prob1intervals[i]),]
#    n=dim(dat)[1]
#    mid2[i] <- ceiling((dat$mid[1]+dat$mid[n])/2)
#  }

  predprob_df_temp$predBound2 <- ifelse(predprob_df_temp$baseNum %in% c$medoids, "Yes", "No")

  dat2 <- predprob_df_temp[which(predprob_df_temp$predBound2=="Yes"),]

ggplot(predprob_df_temp, aes(x=baseNum, y=PredProb)) +
     geom_line(size=.5)+
     #geom_smooth(method = "loess", size = 5, color="blue")
	   geom_vline(data=dat1, aes(xintercept=baseNum, 
             color=as.factor(PredProb)),
             size=.75,
             show.legend = TRUE)+
     geom_vline(data=dat2, aes(xintercept=baseNum, 
             color=predBound2),
             size=.75,
             show.legend = TRUE)+
     scale_color_manual(name = '', 
         values =c("red", "green"),
         labels = c('Predicted Region',
                    'Predicted Boundary'))+
     xlab("Base Pair") +
     ylab("Predicted Probability") +
     theme_minimal() +
     theme_bw() +
     theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        #strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "bottom")

#dat3 <- predprob_df_temp[which(predprob_df_temp$predBound2=="Yes"),]
#dat3$predBound2 <- "T"

#ggplot() + 
#  geom_line(data=predprob_df_temp, aes(x=baseNum, y=PredProb), 
#              color='black',
#              size=.5)+
#  geom_vline(data=dat1, aes(xintercept=baseNum, 
#             color=as.factor(PredProb)),
#             size=.75,
#             show.legend = TRUE)+
#  geom_vline(data=dat2, aes(xintercept=baseNum, 
#             color=predBound),
#             size=.75,
#             show.legend = TRUE)+
#  geom_vline(data=dat3, aes(xintercept=baseNum, 
#             color=predBound2),
#             size=.75,
#             show.legend = TRUE)+
#  xlab("Base Pair") +
#  ylab("Predicted Probability") +
#  scale_color_manual(name = '', 
#         values =c("red", "blue", "green"),
#         labels = c('Predicted Region',
#                    'New Predicted Boundary',
#                    'Midpoint'))+
#  theme_minimal() +
#  theme_bw() +
#  theme(axis.text.x = element_text(size=15),
#        axis.text.y = element_text(size = 15),
#        axis.title.x = element_text(size = 20),
#        axis.title.y = element_text(size = 20),
#        #strip.text.x = element_text(size = 15),
#        #panel.spacing = unit(2, "lines"),
#        legend.text=element_text(size=15),
#        legend.title=element_text(size=20),
#        plot.title = element_text(size=20),
#        legend.position = "bottom")
